Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-04 bbbq_article.tex
Add MHC-II elution study

To determine the percentages of epitopes overlapping
with TMHs, we use reference proteomes of 
a human, viral and bacterial nature.
An overview of Uniprot IDs is shown in table \ref{tab:uniprot_ids}.
The human reference proteome is the same as used previously (\cite{bianchi2017}).

@@

@@

To determine the percentages of MHC-I and MHC-II epitopes overlap
with TMHs, we used mostly the same analysis as described in \cite{bianchi2017}.
To summarize: from a proteome all possible 9-mers are derived. For each
of these peptides, it is measured if it has been part of a 
TMH (at least overlapping 1 residue), 
as well as if the peptide is a binder to an MHC-I haplotype.
Because the percentage of TMH residues is known, a binomial test can be
used to determine if TMH-derived peptides are as likely to be a binder
as expected by chance (the null hypothesis), or that TMHs are indeed an
overrepresented source of epitopes (as found by \cite{bianchi2017}).

@@

>>>>

To determine the percentages of epitopes overlapping
with TMHs, we use reference proteomes of 
a human, viral and bacterial nature.
An overview of Uniprot IDs is shown in table \ref{tab:uniprot_ids}.
Instead of using the full human reference proteome, we
use the representative human reference proteome 
as used previously (\cite{bianchi2017}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Elution studies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To determine if epitopes derived from TMHs are presented at all,
we started from epitopes sequenced from elution studies
for MHC-I \cite{schellens2015comprehensive} 
and MHC-II \cite{bergseng2015different}.
For each epitope, the human representative reference proteome
was searched for its origin.
We kept only the epitopes of which were found exactly once
on the proteome.
We predicted the topology of the proteome
and counted how often the epitopes overlapped
with a predicted TMH.
In this analysis, both TMHMM and 
PureseqTM (see section 'Prediction software used') 
were used to predict the topology.
The full analysis can be found
at \url{https://github.com/richelbilderbeek/bbbq_article_issue_157}.

@@

To determine the percentages of MHC-I and MHC-II epitopes overlap
with TMHs, we used mostly the same analysis as described in \cite{bianchi2017}.
To summarize: from a proteome all possible 9-mers are derived. For each
of these peptides, it is measured if it has been part of a 
TMH (at least overlapping 1 residue), 
as well as if the peptide is a binder to an MHC-I haplotype.
For MHC-II, 15-mers are used, as these are the most occurring
epitope length \cite{bergseng2015different}.

Because the percentage of TMH residues is known, a binomial test can be
used to determine if TMH-derived peptides are as likely to be a binder
as expected by chance (the null hypothesis), or that TMHs are indeed an
overrepresented source of epitopes (as found by \cite{bianchi2017}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Elution studies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
